Silver Ion Chroma

### 2020-12-16 silver_ion_chroma.Rmd
fixed typo

---
title: "Silver Ion Chroma"
author: "Tristan Caro"
date: "12/10/2020"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

# Summary

@@

# Protocol

@@

### Discovery Ag-Ion Column Chromatography

@@

```{=html}
<!-- -->
```
    Autosampler Position: Sample
    37: Cyclohex Blank
    38: TC-BAMES-2
    39: BAMES F1 Disc
    40: BAMES F2 Disc
    41: BAMES F3 Disc
    42: BAMES F1 Nitr
    43: BAMES F2 Nitr
    37: Cyclohex Blank

@@

# Data

@@

## Data Import

@@

## Data Cleanup

@@

## Overview Plot

@@

## Individual Plots

>>>>

---
title: "Silver Ion Chroma"
author: "Tristan Caro"
date: "12/16/2020"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

# Silver Ion Chroma (12/10/2020)

## Summary

> NOTE: BAME concentrations were not correct. See \`modified_silver_ion_chroma.Rmd\`

@@

### Protocol

@@

#### Discovery Ag-Ion Column Chromatography

@@

<!-- -->

    Autosampler Position: Sample
    37: Cyclohex Blank
    38: TC-BAMES-2
    39: BAMES F1 Disc
    40: BAMES F2 Disc
    41: BAMES F3 Disc
    42: BAMES F1 Nitr
    43: BAMES F2 Nitr
    37: Cyclohex Blank

@@

## Data

@@

### Data Import

@@

### Data Cleanup

@@

### Overview Plot

@@

### Individual Plots
